The Unicode Cookbook \linebreak for Linguists

### 2018-06-05 book/chapters/implementation.tex
deals with Github vs GitHub

First, in Section \ref{installing-python-and-r} we explain how to install Python\footnote{\url{https://www.python.org/}} and R.\footnote{\url{https://www.r-project.org/}} Then in Sections \ref{python-implementations} and \ref{r-implementation}, we discuss our Python and R software packages, respectively. In addition to the material presented here to get users started, we maintain several case studies online that illustrate how to use orthography profiles in action. For convenience, we make these recipes available as Jupyter Notebooks\footnote{\url{http://jupyter.org/}} in our Github repository.\footnote{\url{https://github.com/unicode-cookbook/}} In the final section in this chapter, we also briefly describe a few recipes that we do not go into detail in this book.

@@

Once you have R or Python (or both) installed on your computer, you are ready to use the orthography profiles software libraries presented in the next two sections. As noted above, we make this material available online on Github,\footnote{\url{https://github.com/}} a web-based version control system for source code management. Github repositories can be cloned or downloaded,\footnote{\url{https://help.github.com/articles/cloning-a-repository/}} so that you can work through the examples on your local machine. Use your favorite search engine to figure out how to install Git on your computer and learn more about using Git.\footnote{\url{https://git-scm.com/}} In our Github repository, we make the material presented below (and more use cases described briefly in Section \ref{use-cases}) available as Jupyter Notebooks. Jupyter Notebooks provide an interface where you can run and develop source code using the browser as an interface. These notebooks are easily viewed in our Github repository of use cases.\footnote{\url{https://github.com/unicode-cookbook/recipes}}

@@

You can also install the \texttt{segments} package with from the Github repository:\footnote{\url{https://github.com/cldf/segments}}

@@

% In closing, using Github to share code and data provides a platform for sharing scientific results and it also promotes a means for scientific replicability of results. Moreover, we find that in cases where the scientists are building the to tools for analysis, open repositories and data help to ensure that what you see is what you get.

>>>>

First, in Section \ref{installing-python-and-r} we explain how to install Python\footnote{\url{https://www.python.org/}} and R.\footnote{\url{https://www.r-project.org/}} Then in Sections \ref{python-implementations} and \ref{r-implementation}, we discuss our Python and R software packages, respectively. In addition to the material presented here to get users started, we maintain several case studies online that illustrate how to use orthography profiles in action. For convenience, we make these recipes available as Jupyter Notebooks\footnote{\url{http://jupyter.org/}} in our GitHub repository.\footnote{\url{https://github.com/unicode-cookbook/}} In the final section in this chapter, we also briefly describe a few recipes that we do not go into detail in this book.

@@

Once you have R or Python (or both) installed on your computer, you are ready to use the orthography profiles software libraries presented in the next two sections. As noted above, we make this material available online on GitHub,\footnote{\url{https://github.com/}} a web-based version control system for source code management. GitHub repositories can be cloned or downloaded,\footnote{\url{https://help.github.com/articles/cloning-a-repository/}} so that you can work through the examples on your local machine. Use your favorite search engine to figure out how to install Git on your computer and learn more about using Git.\footnote{\url{https://git-scm.com/}} In our GitHub repository, we make the material presented below (and more use cases described briefly in Section \ref{use-cases}) available as Jupyter Notebooks. Jupyter Notebooks provide an interface where you can run and develop source code using the browser as an interface. These notebooks are easily viewed in our GitHub repository of use cases.\footnote{\url{https://github.com/unicode-cookbook/recipes}}

@@

You can also install the \texttt{segments} package with from the GitHub repository:\footnote{\url{https://github.com/cldf/segments}}

@@

% In closing, using GitHub to share code and data provides a platform for sharing scientific results and it also promotes a means for scientific replicability of results. Moreover, we find that in cases where the scientists are building the to tools for analysis, open repositories and data help to ensure that what you see is what you get.
